---
title: "Assignment 2-3: Further exploration of Questions 2.1 and 2.2"
author: "Your Name"
date: "Today's date"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Due Sunday, March 22 @ midnight through Github**

Continue refinining your data displays and survey-weighted models to answer 

**Question 2.1: What factors measured in the NYC HANES survey are associated with having hypertension?**

You will want to think about what variables will be important to look at for examining the risk of hypertension, select these variables from the NYC HANES data set, recode and clean them, and then make some visualizations to examine the relationships among these variables. Think about choosing data displays that directly inform your later modeling choices.

You will then want to use the `svydesign()` function to create an appropriate survey-weighted data set to use for your modeling analysis. You will need to be sure to include a variable with the appropriate survey weights in your data set.

Then, use the `svyglm()` function to fit a logistic regression model, with hypertension as the outcome, to continue to explore the relationships among the variables in your data set in a modeling framework. You will want to consider the variables you include based on your data visualizations or other reasons.

Think about the variables that are included in your model and consider whether you want to include all of them, or drop some. You can use some of the tools we talked about in class to do this.

Write a few sentences interpreting the outputs of your final model. (If you included many variables, you don't need to write about all of them here.)



Using this final model, begin to answer

**Question 2.2: How do our estimates from survey-weighted logistic regression differ from those where we ignore survey weights?**

You'll fit a standard logisitic regression and then you will want to figure out a nice data display to allow comparison of the model results. 

You should complete this assignment in this .Rmd file.  Any text you want to include should be written outside of the code chunks.  Any code must be written inside of the code chunks.

When you want to test and run your whole assignment, you can click the "Knit" button to create an HTML document with your work.

All code to read in and clean the data, and create your data display must be included in this document for it to knit properly.  That is, this document is a stand-alone document that shows all of the data analysis steps starting with the raw data.  It's helpful to periodically knit your document as you work to be sure you've included all the necessary code.

**Do the following things: **

1. Read in the NYC HANES data set and store it into an object called `dat`.  (Note, in this project the data is in a folder called `data` in the main project directory.)
```{r}
library(haven)
dat <- read_sas('data/d.sas7bdat')
dim(dat)

```

2. You will want to select some subset of variables from this data set. To know which ones you want, you can refer to the materials from class and the [Variable Codebook](http://nychanes.org/wp-content/uploads/sites/6/2019/01/28283961_NYC-HANES_codebook_Public_V3_011019.pdf){target="_blank"}. If you want to recode any of the variables in the data set, as we did in the class notes, you can do that in the code chunk here as well.
```{r}
### put recoding data here
### you can use comments like this to describe what you are doing

```

3. Include the code needed to make your data display here.  While working on your assignment, you might try lots of different things.  Please only include the code for the final display that you are submitting for your assignment below (delete the other things you have tried).
```{r}
### put code to create data display here

```

4. Write a couple of sentences interpreting your display in context of the question of interest:

Write your text here.


5. Use the `svydesign()` and `svyglm()` functions to create a survey-weighted object and fit an initial survey-weighted logistic regression.

```{r}
### put code for survey-weighted analysis here

```

6. Interpret the output of your survey-weighted logistic regression, including a description of your model selection procedure.

Write your text here.

7. Fit the same model using un-weighted logistic regression and compare the results using some kind of data display. Discuss what you see.


FINALLY:  When you are ready to submit your assignment, do ALL of the following:

* First, knit your .Rmd file to see if it will compile.  If it doesn't knit, you can still follow the steps below to submit your assignment, but please try to resolve the knitting issues before you submit.  You can reach out to us at phbiostats@jhu.edu for help!
* Next you need to **commit** the changes you've made to the document.  Click the colorful Git button at the top of the RStudio window and select "Commit" from the menu.
* In the window that opens, **stage** your changes by clicking the check boxes next to the `Asst2-2.Rmd` and `Asst2-2.html` files.
* In the "Commit message" box, type a short description of what changes you've made, something like: `Completed assignment`
* Click the "Commit" button on the bottom right.
* You'll see a window that will tell you about the changes that you've made.  Click "Close" to close the window.  You've successfully committed! You can close this commit window now.
* After committing, you must **push** your changes to the repository on Github.  Do this by clicking the colorful Git button again and select "Push Branch".  
* Again, you'll see a window open that tells you your changes have been pushed!
* If you want, you can look at your repository on [Github.com](https://github.com/) and should be able to see your changes there!  
* You've successfully submitted your assignment :)

